\section{Introduction}

People are involved more and more in trading of currencies these days. Amongst those markets, of the biggest buying and selling platforms are cryptocurrency trading and the foreign exchange marketplace (Forex).
Although cryptocurrency promises better returns than foreign exchange, Forex gives solid, especially secured, and relatively regulated trading in comparison to cryptocurrency trading.
As a result, in latest years, the Forex market has attracted pretty a lot of interest from researchers all over the world. Different kinds of studies have been performed to accomplish the task of predicting future Forex currency prices accurately.

Researchers have been involved primarily in neural networks models, pattern-based approaches, and optimization techniques. 
The emergence of artificial neural networks performed a massive function in foreign exchange rate prediction. During our evaluation of related works, we discovered that many deep learning algorithms, such as gated recurrent unit (GRU) and long short term memory (LSTM), have been explored and exhibit potential in time sequence prediction.

The foreign exchange market, is the world’s largest foreign money trade market with over $5.1$ trillion of trade exchange per day. It is recognized to be very complicated and volatile. Currency trading occurs 24 h a day (weekend excluded), however the buying and selling time is divided into 4 fundamental time zones. Each of these zones has its specific opening hours and closing hours.
Forex is divided into three specific categories: majors, minors, and exotics. Majors are the most traded currencies which are priced in opposition to the USD and occupy the majority of the Forex market. 

Each Forex pair has its opening price, highest price, lowest price, and closing price based on the trading session. For security reasons, it is now not possible for one person to go to, register with, and purchase from the Forex market,  but each individual needs to use third party like brokers, who are humans or corporations that have admission to the Forex market and are capable to buy or sell currencies. In the Forex market, solely two alternatives are available, either buying currencies or selling. 

%Recent years have viewed a lot of researches in the Forex market foreign money rate prediction. 
Predicting the Forex market has been a key goal of investigators over the preceding couple of decades. There are two methods to forecast the market: fundamental and technical analysis. \textbf{Fundamental analysis} considers many factors, such as the financial system and political state of a country, the popularity of a company, all inner and exterior buying and selling news, etc. \textbf{Technical analysis} concentrates predicting the Forex market based totally on historic data, in particular, the highest price, lowest price, opening price, and closing price of a currency and the volume traded on a particular day. In this work, we concentrate on technical analysis.

Existing techniques are not appropriate for all currency pairs and may provide better effects for only a few randomly selected ones in specific time-frames. Also, most of existing researches are evaluated only considering their prediction error, without considering the entire effect on a broader trading system where the decision to open a position, i.e. to invest, is as important as the decision to close the position. 

In this article, we propose our reusable trading system extensively trained on historical data, measured at 4-hours intervals candlesticks, of 6 currency pairs: 4 major pairs like GBP/USD, EUR/USD, USD/CHF and USD/JPY, and 2 minor pairs like EUR/GBP and GBP/JPY.  The entire dataset spans from 01-01-2010 till 30-04-2021 and we conducted 
thorough experiments on the aforementioned currency pairs on 3 test sets constituted by the entire year 2019, the entire year 2020 and current time interval for year 2021 (from 01-01 till 30-04) for all the 6 currency pairs. For almost all currency pairs during the three long considered time intervals our system has produced stable and high profitable results. We conclude that the best strategy is to invest simultaneously on all of the currency pairs to reduce the loss risk and stay profitable, since, in financial domain, it is not easy to construct a stable mechanism that always generates profit. 

The remainder of the paper is arranged as follows. Section~\ref{sec:2} presents numerous techniques that have been examined in preceding years and can be categorized into several categories: regression strategies, optimization strategies, neural networks, and others. Section~\ref{sec:3} introduces the fundamentals of Forex, trading system such as Meta Trader 5 as well as technical indicators and trading rules. Section~\ref{sec:tradsys} elaborates on our proposed trading system. Section~\ref{sec:5} presents the results of the experiments on historical data, measured at 4-hours intervals candlesticks, of 6 currency pairs on a long time-frame that spans from 01-01-2010 till 30-04-2021. We conclude our article discussing in the last section the results and possible future directions.
