\section{Preliminaries}

\subsection{Trading}
In first instance, an order is a request to make a trade to open a position.
A trade is made when the order is matched to a counterpart, i.e a buyer has found a seller, or vice versa.
Once a trade is opened, it constitutes a position. A position is exposure to the market and will move the balance in the account up or down in line with market movements.

Finally, placing an order to close a position will result in an trade opposite to the direction initially took, e.g. if we initially bought, now we sell to close.

\subsection{Trading System: Meta Trader 5}

\subsection{Technical indicators}
In our trading system, XX technical indicators are used as the basis of trading rules. These technical indicators are: Adaptive Moving Average, Average Directional Moving Index, Bollinger Bands, Double Exponential Moving Average, Envelope Moving Avarage, Parabolic SAR, Fractal Adaptive Moving Avarage, Standard Deviation, Triple Exponential Moving Average, Avarage True Range, Bears Power, Bulls Power, MACD (Moving Average Convergence Divergence), Stochastic oscillator, William' Percentage Range, Momentum, RSI (Relative Strength Index), and Heiken Ashi Candles.

\subsection{Trading Rules}

\subsubsection{Trading Rules with Dynamic Channels}

Many operating strategies built for short-term trading use signals provided by what are known in technical jargon as 'dynamic channels'. In some cases the strategies are of type trend following, that is they aim to follow the main trend present on the market, in other cases instead they are of type reversal in how much they try to take advantage of a possible reversal of trend.
The principle of base of these operating techniques is based on the individualization of some bands of oscillation (envelopes) that:

\begin{itemize}
\setlength\itemsep{0.3em}
\item Contain for the greater part of the time the movement of the prices.
\item They concur to characterize the trend followed from the prices.
\item They supply interesting reversal signals.
\end{itemize}

These channels are dynamic in how much, measuring (even if in various way) the present instability on the market, they are adapted to the movements (cyclical) carried out from the prices, that alternate in fact phases of consolidation (in which the instability is reduced) to directional/impulsive phases (in which the instability increases in meaningful way). The technique of the bands requires the identification of:

\begin{itemize}
\setlength\itemsep{0.3em}
\item A central reference average, which serves to identify and exploit the primary trend present in the market;
\item A lower band and an upper band, which constitute respectively a support and a resistance of dynamic type (as they move according to the volatility recorded on the market) and which contain the movement of prices.
\end{itemize}

When volatility is low the two bands narrow and approach prices (the channel width is reduced), when volatility is high the two bands widen and move away from prices (the channel width increases). 

We begin therefore with the description of the more used dynamic channels, beginning from the Channel of Donchian and the Bands of Stoller. 

\paragraph{\textbf{The Donchian channel}}\mbox{}

One of the first operational techniques based on the use of channels was invented by Richard Donchian who built a trend following system based on the identification of the highs and lows of the last 20 days (the original system was based on the \textit{Donchian 4-week rule}). With this technique:

\begin{itemize}
\setlength\itemsep{0.3em}
\item Long positions were opened when prices exceeded the highest high of the last 20 days.
\item One would open short positions when they fall below the lowest low of the last 20 days.
\end{itemize}  

With this technique one goes in search of the classic breakout signals that can initiate a directional movement. Draft however of a system that has been applied with success during the years $'80$ on the market of the commodities (where the tendencies were stable and consisting) but that in the course of the time has diminished its efficiency. For this reason it has been gone to the search of techniques in a position to exploiting also the frequent and unexpected reversals of tendency that are verified when the prices catch up important zones of resistance and/or support.

\paragraph{\textbf{Stoller Bands}}\mbox{}

An experienced commodities trader, Manning Stoller, has constructed an operating technique (Stoller Average Range Channels, STARC) which uses the concept of the Average True Range (ATR). This differs from the simple daily range (the difference between the high and the low price) in that it also takes into account whether there is a gap-up or gap-down.
The ATR is the greater of these three differences:

\begin{itemize}
\setlength\itemsep{0.3em}
\item Today's maximum price minus today's minimum price.
\item Today's maximum price minus yesterday's closing price.
\item Yesterday's closing price minus today's low price.
\end{itemize}  


To calculate the Stoller Bands, a 6-period moving average is calculated, to which the 15-period moving average of the Average True Range multiplied by two is added (to obtain the upper band) and subtracted (to obtain the lower band).
There are therefore three reference lines:

\begin{itemize}
\setlength\itemsep{0.3em}
\item The Upper Band equals to the 6-period moving average plus $(ATR*2)$.
\item The Central Average equals to the 6-period moving average.
\item The Lower Band equals to the 6-period moving average minus $(ATR*2)$.
\end{itemize}  


The difference from the technique proposed from Donchian (of trend following type), the Stoller Bands come used in order to obtain of the signals of reversal. In particular:

\begin{itemize}
\setlength\itemsep{0.3em}
\item Short signals are obtained when prices go beyond the upper band and draw a reversal short bar (for example a shooting).
\item Long signals are obtained when the prices come down under the inferior band and draw a bar of reversal long (as an example a hammer).
\end{itemize} 
